Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
add ref for zens
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58592 72bbbca6-d526-0410-a7d9-f06f51895060

We trained models based on two approaches, the first being phrase-based machine translation
CITEXXX and the second on character-based machine translation \cite{nakov2012,TiedemannEAMT2009}.

>>>>

We trained models based on two approaches, the first being phrase-based machine translation
\cite{zens2002} and the second on character-based machine translation \cite{nakov2012,TiedemannEAMT2009}.
